Stochastic blockmodeling of relational event dynamics

### 2012-05-31 docs/discussion.tex
Small paper edits.

%% TODO: Discuss scalability.
%% TODO: Describe and include posterior predictive checks.

\begin{figure}[t]
\centering
\begin{subfigure}[b]{0.35\textwidth}
\centering
\includegraphics[scale=.5]{../figs/eckmann-small/example-obs-stats}
%\caption{Observed counts}
\end{subfigure}
\qquad
\begin{subfigure}[b]{0.35\textwidth}
\centering
\includegraphics[scale=.5]{../figs/eckmann-small/example-estimates}
%\caption{Samples of $\beta_{p,k,l}$}
\end{subfigure}

\caption{%Observed counts versus model estimates from Eckmann email data.
 Left: Observed statistics across all dyadic email interactions between  members of group 1 and group 3.  Right: Posterior samples of the corresponding $\beta_{p,1,3}$ and $\beta_{p,3,1}$.  In addition to finding differences in mean activity for these dyads, estimates suggest events from 3 to 1 have a higher propensity for \texttt{ab-by} transitions.}
\label{fig:posteriorparams}
\end{figure}

>>>>

% \begin{figure}[t]
% \centering
% \begin{subfigure}[b]{0.35\textwidth}
% \centering
% \includegraphics[scale=.5]{../figs/eckmann-small/example-obs-stats}
% %\caption{Observed counts}
% \end{subfigure}
% \qquad
% \begin{subfigure}[b]{0.35\textwidth}
% \centering
% \includegraphics[scale=.5]{../figs/eckmann-small/example-estimates}
% %\caption{Samples of $\beta_{p,k,l}$}
% \end{subfigure}

% \caption{%Observed counts versus model estimates from Eckmann email data.
%  Left: Observed statistics across all dyadic email interactions between  members of group 1 and group 3.  Right: Posterior samples of the corresponding $\beta_{p,1,3}$ and $\beta_{p,3,1}$.  In addition to finding differences in mean activity for these dyads, estimates suggest events from 3 to 1 have a higher propensity for \texttt{ab-by} transitions.}
% \label{fig:posteriorparams}
% \end{figure}
